Formalizing Stack Safety as a Security Property

### 2023-02-03 submission5/core.tex
edits in 5

On the other hand, if the address of an object is taken directly and passed it as a
pointer, we have no way obvious way to limit the scope of such sharing.
We treat this scenario as the caller allocating a ``public''
object that receives no protection. We extend the \(\mathbf{alloc}\) operation
with a boolean flag, where {\bf t} indicates
that the allocation is public, and {\bf f} that it is private.
If space for multiple objects is allocated in a single step,
that step can make multiple allocation operations, each labeled appropriately.
Public objects are labeled \(\public\) rather than \(\object\), so they are
never sealed at a call (\cref{sfig:publicalloc}).

@@

>>>>

If the address of an object is taken directly and passed as a
pointer, we simply classify the object as ``public'' and give it no protection against
access by other functions. We extend the \(\mathbf{alloc}\) operation
with a boolean flag, where {\bf t} indicates
that the allocation is public, and {\bf f} that it is private.
If space for multiple objects is allocated in a single step,
that step can make multiple allocation operations, each labeled appropriately.
Public objects are labeled \(\public\) rather than \(\object\), so they are
never sealed at a call (\cref{sfig:publicalloc}).
Providing more fine-grained control over sharing is desirable, but
seems to require a considerably more complex model; \cref{app:ptr} describes one
approach, based on capabilities.

@@

\apt{good place to detail the needed changes in interpretation of \cref{tab:props}.}
